Astrophysical calibration of gravitational-wave detectors

### 2015-11-09 docs/cosmic_cal.tex
Changes for submission to arXiv

\IfFileExists{revtex4-1.cls}{\documentclass[prd, twocolumn, lengthcheck,
superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4-1}}{
\IfFileExists{revtex4.cls}{\documentclass[prd, twocolumn, lengthcheck,
superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4}}{}
}

@@

%% ----- input git-version tag
\input{tag.tex}

>>>>

%\IfFileExists{revtex4-1.cls}{\documentclass[prd, twocolumn, lengthcheck,
%superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4-1}}{
%\IfFileExists{revtex4.cls}{\documentclass[prd, twocolumn, lengthcheck,
%superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4}}{}
%}
\documentclass[prd, twocolumn, lengthcheck, superscriptaddress, showpacs, letterpaper, nofootinbib]{revtex4-1}

@@

%% ----- input git-version tag
%\input{tag.tex}
